### 2020-03-10 CalNotes.tex
CLT Poisson Homogenization2

@@

Let us first introduce a technical Lemma.
\begin{lemma}\label{lem:CLT} Let $\mathcal L_\epl$ be the generator of the couple $(X^\epl, Z^\epl)^\top$, i.e.,
	\begin{equation}
		\mathcal L_\epl = -\left(\alpha \cdot V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx}.
	\end{equation} 
	Moreover, let $\rho^\epl$ be the invariant measure of $(X^\epl, Z^\epl)^\top$ and $\Phi^\epl\colon \R^2 \to \R^N$ be the solution of 
	\begin{equation}\label{eq:CLT_Poisson}
		-\mathcal L_\epl \Phi^\epl = \chi^\epl -  \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)],
	\end{equation}
	for $\chi^\epl \colon \R^2 \to \R^N$ satisfying $\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl)] = 0$. Then, it holds
	\begin{equation}\label{eq:CLT_PoissonIto}
		\frac{1}{T} \int_0^T  \chi^\epl(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)] - \frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T},
	\end{equation}
	where
	\begin{equation}\label{eq:CLT_PoissonRemainders}
		R^\epl(T) \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl(T) \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
	\end{equation}
	Moreover, it holds
	\begin{equation}\label{eq:CLT_Equiv}
		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)] = \E^{\rho^\epl}
		\begin{aligned}[t]
		[&\chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
		&+ \Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)].
		\end{aligned}
	\end{equation}	
\end{lemma}
\begin{proof} The proof of \eqref{eq:CLT_PoissonIto} and \eqref{eq:CLT_PoissonRemainders} is an application of the Itô formula (see e.g. \cite[Remark 6.17]{PaS08}). For \eqref{eq:CLT_Equiv}, it is possible to show that since $\mathcal L_\epl^*\rho^\epl = 0$ it holds 
	\begin{equation}
		\mathcal L_\epl^* (\Phi^\epl \rho^\epl) = 2 \sigma \rho^\epl \partial_{xx}^2 \Phi^\epl - \rho^\epl \mathcal L_\epl\Phi^\epl + 2 \sigma \partial_x \Phi^\epl \partial_x \rho^\epl.
	\end{equation}
	Therefore, an integration by parts yields 
	\begin{equation}
	\begin{aligned}
		\E^{\rho^\epl}[\mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl)] &= 	\int_{\R}\int_{\R} \Phi^\epl \otimes \mathcal L_\epl^*\left(\Phi^\epl \rho^\epl\right) \dd x \dd z \\
		&= -\int_{\R}\int_{\R}\Phi^\epl \otimes \mathcal L_\epl \Phi^\epl \rho^\epl \dd x \dd z- 2\sigma \int_{\R}\int_{\R} \partial_x \Phi^\epl \otimes \partial_x \Phi^\epl \rho^\epl \dd x \dd z\\
		&= 
		\begin{aligned}[t]
		&-\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl)] \\
		&- 2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)].
		\end{aligned}
	\end{aligned}
	\end{equation}
	Finally, since $\E^{\rho^\epl}[\Phi(X^\epl, Z^\epl)] = 0$ 
	\begin{equation}
	\begin{aligned}
		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)] &= -\E^{\rho^\epl}
		\begin{aligned}[t]
		[&\mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
		& + \Phi^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl)]
		\end{aligned}
		\\
		&= \E^{\rho^\epl}
		\begin{aligned}[t]
		[&\chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
		&+ \Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)],
		\end{aligned}
	\end{aligned}
	\end{equation}
	which is the desired result.
\end{proof}

We can now proceed with the main proof.
\begin{proof}[Proof of Theorem \ref{thm:CLT}] Let us introduce the notation
	\begin{equation}\label{eq:CLT_DefMEps}
	\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathcal M_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ],
	\end{equation}
	and the notation
	\begin{equation}
	\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]\
	\end{equation}
	and let us remark that from the proof of Theorem \ref{thm:mainTheorem} one can deduce the equalities
	\begin{equation}\label{eq:CTL_A}
	A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
	\end{equation}
	and
	\begin{equation}\label{eq:CTL_alpha}
	\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathfrak p_\epl \right).
	\end{equation}
	Let us furthermore remark that the decomposition \eqref{eq:alphaDecomposition} yields
	\begin{equation}
	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T} \left(\alpha - A + I_1^\epl - I_2^\epl\right).
	\end{equation}
	Replacing the expression for $A$ and $\alpha$ given in \eqref{eq:CTL_A} and \eqref{eq:CTL_alpha}, we get
	\begin{equation}
	\begin{aligned}
	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) &= \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \\
	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
	&- \sqrt{T} I_2^\epl(T).
	\end{aligned}
	\end{equation}
	\corr{Third term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
	\begin{equation}
	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl(T),
	\end{equation}
	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
	\begin{equation}
	Q^\epl(T) \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
	\end{equation}
	is a martingale whose quadratic variation is given by
	\begin{equation}
	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
	\end{equation}
	Since the ergodic theorem guarantees that 
	\begin{equation}
	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
	\end{equation}
	the martingale central limit theorem gives 
	\begin{equation}
	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl(T) = \Xi^\epl, \quad \text{in law},
	\end{equation}
	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
	Now, by the ergodic theorem 
	\begin{equation}
	\lim_{T \to \infty} \widetilde M^{-1} = \mathcal M_\epl^{-1}, \quad \text{a.s.}
	\end{equation}
	Therefore, we have by Slutsky's theorem that
	\begin{equation}
	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
	\end{equation}
	where the covariance matrix $\Gamma^\epl$ is given by
	\begin{equation}
	\Gamma^\epl = 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\mathcal M_\epl^{-\top}.
	\end{equation}
	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.

	\corr{Idea for the first term:} Let us introduce the notation
	\begin{equation}
	J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
	\end{equation}
	and let us remark that we can rewrite
	\begin{equation} \label{eq:decomposition_first_term}
	\begin{aligned}
	J_1^\epl(T) = \sqrt{T} &\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\\
		&\quad \times \left(\frac1T \int_0^T \left( \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t)	- V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \dd t	 \right).
	\end{aligned}
	\end{equation}
	Let us denote by $\Phi^\epl$ the solution of \eqref{eq:CLT_Poisson} in Lemma \ref{lem:CLT} with right hand side
	\begin{equation}
	\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
	\end{equation}
	and note that $\E^{\rho^\epl}[\chi^\epl(X^\epl,Z^\epl)] = 0$. Then we have
	\begin{equation}
	J_1^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( -\frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T} \right),
	\end{equation}
	where $R^\epl(T)$ and $S^\epl(T)$ are defined in \eqref{eq:CLT_PoissonRemainders}. Since \corr{$R^\epl(T)$ is bounded independently of $\epl$ (is it clear?)}, we first get by the ergodic theorem
	\begin{equation}
	\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R^\epl(T)}{\sqrt{T}} = 0, \quad \text{a.s.}
	\end{equation}
	Repeating the same reasoning as for $Q^\epl(T)$ and employing the ergodic theorem and the Slutsky's theorem, we get 
	\begin{equation}
	\lim_{T \to \infty} J_1^\epl(T) = \lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S^\epl(T)}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	\end{equation}
	where the covariance is given by due to \eqref{eq:CLT_Equiv}
	\begin{equation}
	\begin{aligned}
	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl) + \chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
	\end{aligned}
	\end{equation}
	\corr{For the covariance $\Gamma_1^\epl$ we don't know how it behaves in the limit $\epl \to 0$. It would be nice if it was vanishing, but it involves the solution $\Phi^\epl$, which has r.h.s. depending of $\epl$. We noticed that the homogenized problem of
	\begin{equation}
		-\mathcal L_\epl \Phi^\epl = \chi^\epl,
	\end{equation}
	is given by
	\begin{equation}
		-\mathcal L_0 \Phi^0 = 0,
	\end{equation}
	whose zero-mean solution is $\Phi^0 = 0$.}

>>>>

\begin{equation}\label{eq:CellProblem}

@@

Let us first introduce a technical Lemma.
\begin{lemma}\label{lem:CLT} Let $\mathcal L_\epl$ be the generator of the couple $(X^\epl, Z^\epl)^\top$, i.e.,
	\begin{equation}
		\mathcal L_\epl = -\left(\alpha \cdot V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx}.
	\end{equation} 
	Moreover, let $\rho^\epl$ be the density of the invariant measure of $(X^\epl, Z^\epl)^\top$ and $u^\epl\colon \R^2 \to \R^N$ be the solution of 
	\begin{equation}\label{eq:CLT_Poisson}
		-\mathcal L_\epl u^\epl = \chi^\epl -  \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)],
	\end{equation}
	satisfying $\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl)] = 0$ for $\chi^\epl \colon \R^2 \to \R^N$. Then, it holds
	\begin{equation}\label{eq:CLT_PoissonIto}
		\frac{1}{T} \int_0^T  \chi^\epl(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)] - \frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T},
	\end{equation}
	where
	\begin{equation}\label{eq:CLT_PoissonRemainders}
		R^\epl(T) \defeq u^\epl(X^\epl_T, Z^\epl_T) - u^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl(T) \defeq \int_0^T \partial_x u^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
	\end{equation}
	Moreover, it holds
	\begin{equation}\label{eq:CLT_Equiv}
		2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)] = \E^{\rho^\epl}
		\begin{aligned}[t]
		[&\chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
		&+ u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)].
		\end{aligned}
	\end{equation}	
\end{lemma}
\begin{proof} The proof of \eqref{eq:CLT_PoissonIto} and \eqref{eq:CLT_PoissonRemainders} is an application of the Itô formula (see e.g. \cite[Remark 6.17]{PaS08}). For \eqref{eq:CLT_Equiv}, it is possible to show that since $\mathcal L_\epl^*\rho^\epl = 0$ it holds 
	\begin{equation}
		\mathcal L_\epl^* (u^\epl \rho^\epl) = 2 \sigma \rho^\epl \partial_{xx}^2 u^\epl - \rho^\epl \mathcal L_\epl u^\epl + 2 \sigma \partial_x u^\epl \partial_x \rho^\epl.
	\end{equation}
	Therefore, an integration by parts yields 
	\begin{equation}
	\begin{aligned}
		\E^{\rho^\epl}[\mathcal L_\epl u^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl)] &= 	\int_{\R}\int_{\R} u^\epl \otimes \mathcal L_\epl^*\left(u^\epl \rho^\epl\right) \dd x \dd z \\
		&= -\int_{\R}\int_{\R}u^\epl \otimes \mathcal L_\epl u^\epl \rho^\epl \dd x \dd z- 2\sigma \int_{\R}\int_{\R} \partial_x u^\epl \otimes \partial_x u^\epl \rho^\epl \dd x \dd z\\
		&= 
		\begin{aligned}[t]
		&-\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl u^\epl(X^\epl, Z^\epl)] \\
		&- 2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)].
		\end{aligned}
	\end{aligned}
	\end{equation}
	Finally, since $\E^{\rho^\epl}[u(X^\epl, Z^\epl)] = 0$ 
	\begin{equation}
	\begin{aligned}
		2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)] &= -\E^{\rho^\epl}
		\begin{aligned}[t]
		[&\mathcal L_\epl u^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
		& + u^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl u^\epl(X^\epl, Z^\epl)]
		\end{aligned}
		\\
		&= \E^{\rho^\epl}
		\begin{aligned}[t]
		[&\chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
		&+ u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)],
		\end{aligned}
	\end{aligned}
	\end{equation}
	which is the desired result.
\end{proof}

\begin{lemma} Let $u^\epl$ be the solution of \eqref{eq:CLT_Poisson} with 
		\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
		\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ].
	Then, $u^\epl \to 0$ \corr{in which sense?} for $\epl \to 0$.
\end{lemma}
\begin{proof} We here present a formal proof based on asymptotic expansion with respect to $\epl$. Let us first remark that by definition
		\E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)] = 0,
	and therefore problem \eqref{eq:CLT_Poisson} reads
		-\mathcal L^\epl u^\epl = \chi^\epl.
	Let us now denote $y = x/\epl$ and write
		u^\epl(x, z) = u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots,
	which implies that
		\partial_x u^\epl &= \partial_x(u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots) \\
		&\quad+ \frac1\epl\partial_y(u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots).
	Let us first remark that from the proof of Theorem \ref{thm:mainTheorem} we have that
		\lim_{\epl \to 0} \mathcal M_\epl^{-1}\mathfrak p_\epl = A - \alpha.
	Replacing $u^\epl$ in \eqref{eq:CLT_Poisson} and grouping the terms of order $\epl^0$, $\epl^{-1}$ and $\epl^{-2}$ we get the system
		L_0 u_0 &= 0, \label{eq:CLT_AsExp1}\\
		L_1 u_0 + L_0 u_1 &= - p'(y) V'(z), \label{eq:CLT_AsExp2}\\
		L_0 u_2 + L_1 u_1 + L_2 u_0 &= \left(V'(z) \otimes V'(x)\right) (A - \alpha),\label{eq:CLT_AsExp3}
		L_0 &= -p'(y) \partial_y + \sigma \partial^2_{yy},\\
		L_1 &= -p'(y) \partial_x - \alpha \cdot V'(x) \partial_y + 2 \sigma \partial^2_{xy}, \\
		L_2 &= 	-\alpha \cdot V'(x) \partial_x - \frac1{\delta}(z - x)	\partial_z + \sigma \partial^2_{xx}.
	Let us first remark that equation \eqref{eq:CLT_AsExp1} is satisfied for $u_0 = u_0(x, z)$ independent of $y$. In particular, the kernel of $L_0$ is made of constants and the kernel of $L_0^*$ is one-dimensional and $\mathrm{Ker}(L_0^*) = \mathrm{Span}\{\rho\}$ where
	\begin{equation}\label{eq:CLT_Invariant}
		\rho(y) = \frac1Z e^{-p(y)/\sigma}, \quad\text{where}\quad Z = \int_0^L e^{-p(y)/\sigma} \dd y,
	where $L$ is the period of $p$. Since $u_0$ is independent of $y$ equation \eqref{eq:CLT_AsExp2} reduces to 
		L_0 u_1 = p'(y)\left(\partial_x u_0 -V'(z)\right).
	Let us remark that the general solution $u_1$ can be written as
		u_1(x,y,z) = \Phi(y)\left(\partial_x u_0(x, z) - V'(z)\right),
	where $\Phi \colon \R \to \R$ satisfies
		-L_0 \Phi = -p'(y).
	Let us remark that this cell problem is the same as \eqref{eq:CellProblem}. We consider now equation \eqref{eq:CLT_AsExp3} and remark that we can rewrite it as
		L_0 u_2 &= (V'(z) \otimes V'(x))(A - \alpha) - \left(2\Phi'(y) - \frac1\sigma p'(y) \Phi(y) + 1\right) \sigma \partial^2_{xx}u_0 \\
		&\quad +\left(\Phi'(y) + 1\right) \left( \alpha \cdot V'(x) \right) \partial_x u_0 - \left(V'(z) \otimes V'(x) \right)\alpha \Phi'(y) + \frac1\delta(z-x) \partial_z u_0.
	By the Fredholm alternative, in order for \eqref{eq:CLT_AsExp3} to have a solution we need the right hand side to have zero-mean with respect to $\rho$ in \eqref{eq:CLT_Invariant}. Therefore, recalling that the homogenization coefficient $K$ in \eqref{eq:K_HOM} is given by
		K = \int_0^L (1 + \Phi'(y))^2 \rho(y) \dd y
	and remarking that integrations by part allow to rewrite $K$ as
		K = \int_0^L (1 + \Phi'(y)) \rho(y) \dd y, \quad  K = \int_0^L \left(2\Phi'(y) - \frac1\sigma p'(y) \Phi(y) + 1\right) \rho(y) \dd y,
	we get
		0 = (V'(z) \otimes V'(x))(A - \alpha - (K - 1)\alpha) - K \sigma \partial^2_{xx}u_0 + \left(K \alpha \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0,
	which, since $A = K\alpha$ and $\Sigma = K\sigma$, implies
		0 = -\Sigma \partial^2_{xx}u_0 + \left(A \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0,

We can now proceed with the main proof.
\begin{proof}[Proof of Theorem \ref{thm:CLT}] Let us introduce the notation
	\begin{equation}\label{eq:CLT_DefMEps}
	\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathcal M_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ],
	\end{equation}
	and the notation
	\begin{equation}
	\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]
	\end{equation}
	and let us remark that from the proof of Theorem \ref{thm:mainTheorem} one can deduce the equalities
	\begin{equation}\label{eq:CTL_A}
	A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
	\end{equation}
	and
	\begin{equation}\label{eq:CTL_alpha}
	\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathfrak p_\epl \right).
	\end{equation}
	Let us furthermore remark that the decomposition \eqref{eq:alphaDecomposition} yields
	\begin{equation}
	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T} \left(\alpha - A + I_1^\epl - I_2^\epl\right).
	\end{equation}
	Replacing the expression for $A$ and $\alpha$ given in \eqref{eq:CTL_A} and \eqref{eq:CTL_alpha}, we get
	\begin{equation}
	\begin{aligned}
	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) &= \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \\
	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
	&- \sqrt{T} I_2^\epl(T).
	\end{aligned}
	\end{equation}
	\corr{Third term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
	\begin{equation}
	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl(T),
	\end{equation}
	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
	\begin{equation}
	Q^\epl(T) \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
	\end{equation}
	is a martingale whose quadratic variation is given by
	\begin{equation}
	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
	\end{equation}
	Since the ergodic theorem guarantees that 
	\begin{equation}
	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
	\end{equation}
	the martingale central limit theorem gives 
	\begin{equation}
	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl(T) = \Xi^\epl, \quad \text{in law},
	\end{equation}
	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
	Now, by the ergodic theorem 
	\begin{equation}
	\lim_{T \to \infty} \widetilde M^{-1} = \mathcal M_\epl^{-1}, \quad \text{a.s.}
	\end{equation}
	Therefore, we have by Slutsky's theorem that
	\begin{equation}
	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
	\end{equation}
	where the covariance matrix $\Gamma^\epl$ is given by
	\begin{equation}
	\Gamma^\epl = 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\mathcal M_\epl^{-\top}.
	\end{equation}
	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.

	\corr{Idea for the first term:} Let us introduce the notation
	\begin{equation}
	J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
	\end{equation}
	and let us remark that we can rewrite
	\begin{equation} \label{eq:decomposition_first_term}
	\begin{aligned}
	J_1^\epl(T) = \sqrt{T} &\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\\
		&\quad \times \left(\frac1T \int_0^T \left( \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t)	- V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \dd t	 \right).
	\end{aligned}
	\end{equation}
	Let us denote by $\Phi^\epl$ the solution of \eqref{eq:CLT_Poisson} with right hand side
	\begin{equation}
	\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
	\end{equation}
	and note that $\E^{\rho^\epl}[\chi^\epl(X^\epl,Z^\epl)] = 0$. Then, by Lemma \ref{lem:CLT}, we have
	\begin{equation}
	J_1^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( -\frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T} \right),
	\end{equation}
	where $R^\epl(T)$ and $S^\epl(T)$ are defined in \eqref{eq:CLT_PoissonRemainders}. Since \corr{$R^\epl(T)$ is bounded independently of $\epl$ (is it clear?)}, we first get by the ergodic theorem
	\begin{equation}
	\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R^\epl(T)}{\sqrt{T}} = 0, \quad \text{a.s.}
	\end{equation}
	Repeating the same reasoning as for $Q^\epl(T)$ and employing the ergodic theorem and the Slutsky's theorem, we get 
	\begin{equation}
	\lim_{T \to \infty} J_1^\epl(T) = \lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S^\epl(T)}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
	\end{equation}
	where the covariance is given by due to \eqref{eq:CLT_Equiv}
	\begin{equation}
	\begin{aligned}
	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl) + \chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
	\end{aligned}
	\end{equation}
	\corr{For the covariance $\Gamma_1^\epl$ we don't know how it behaves in the limit $\epl \to 0$. It would be nice if it was vanishing, but it involves the solution $\Phi^\epl$, which has r.h.s. depending of $\epl$. We noticed that the homogenized problem of
	\begin{equation}
		-\mathcal L_\epl \Phi^\epl = \chi^\epl,
	\end{equation}
	is given by
	\begin{equation}
		-\mathcal L_0 \Phi^0 = 0,
	\end{equation}
	whose zero-mean solution is $\Phi^0 = 0$.}
